# Deducibles

El principal objetivo de los deducibles, es el reducir los costos de atención de los reclamos 
usualmente mediante la exclusión de siniestros usualmente numerosos debidos a reclamos pequeños.
En otras ocasiones, los deducibles están diseñados para incentivar al asegurado para evitar 
y prevenir siniestros por cierto monto límite.

1. Prevención de la pérdida - as the compensation is reduced by a deductible the retention of the 
insured is positive; This makes out a good case for avoiding the loss; 

2. Reducción de la pérdida - the fact a deductible puts the policyholder at risk of obtaining 
only partial compensation provides an economic incentive to reduce the extend of the damage; 

3. Evitar pequeñas pérdidas - where administration costs are dominant for small losses, the 
administration costs will often exceed the loss itself, and hence the insurance company would want 
the policyholder to pay it himself; 

4. Reducción de la prima - premium reduction can be an important aspect for the policyholders, 
they may prefer to take a higher deductible to get a lower premium.


```{r l4c1, include = FALSE}
n <- 1e3
l <- 3
dat <- data.table( id = 1:n, k = rpois( n, lambda = l )  )
# dat <- data.table( id = 1:n, k = rbinom( n, 10, 0.3 )  )
# dat <- data.table( id = 1:n, k = rnbinom ( n, 10, 0.3 )  )

datf <- dat[ , list( fk = .N ), by = k ]
setorder( datf, k )
datf[ , fks := shift( fk, n = 1 ) ]
datf[ , gk := k * fk / fks ]
datf <- datf[ !is.na( gk ) ]
plot( datf$k, datf$gk )
```

```{r l4c2, include = FALSE}
dflm <- lm( formula = gk ~ k, data = datf, method = 'qr' )
a <- coef( dflm )[ 2 ]
b <- coef( dflm )[ 1 ]
p0 <- exp( -b )
k <- seq( 1, 100, 1 )
p <- p0 * cumprod( c( 1, a + b / k ) )
sum( p )
k <- seq( 0, 100, 1 )
sum( dpois( k, lambda = l ) )
EN <- sum( k * p )

plot( k, p, ylim = c( 0, 0.3 ) )
points( k, dpois( k, lambda = b ), col = 'red' )

```